---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

## frailtyr

```{r, cache = FALSE, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "figures"
)
```

frailtyr is a library for fitting shared frailty models with support for general frailty distributions. **This is currently a work in progress**, part of Google Summer of Code 2015.

## Installation

To get started, you can install the package from github using `devtools`.

```{r eval = F}
library(devtools)
install_github("vmonaco/frailtyr")
```

## Clone and build

To create a project in RStudio from this repository, you must have both RStudio and git installed.

* In RStudio, go to File -> New Project -> Version Control -> Git
* Name the project (eg. frailtyr), choose location, and specify the Repository URL as `https://github.com/vmonaco/frailtyr`

More information about [RStudio and git](https://support.rstudio.com/hc/en-us/articles/200532077-Version-Control-with-Git-and-SVN)

Also see the chapter in the [R packages book](http://r-pkgs.had.co.nz/git.html)

### Build everything

To load the package (simulate installing and loading with `library(frailty)`):
```{r eval = F}
devtools::load_all()
```
or shortuct: **Ctrl+Shift+L**

Use this command to build a source package (binary = FALSE by default)
```{r eval = F}
devtools::build()
```

Other usefull commands and shortcuts:

- Build and reload everything: **Ctrl+Shift+B**
- Check the package, `devtools::check()`: **Ctrl+Shift+E**
- Run all tests, `devtools::test()`: **Ctrl+Shift+T**

### Build vignettes

Build the vignettes with the command:
```{r eval = F}
devtools::build_vignettes()
```

Compiled vignettes will reside in `inst/doc`. In particular, see frailtyr.pdf