---
output:
  md_document:
    variant: markdown_github
---

[![Travis-CI Build Status](https://travis-ci.org/vmonaco/frailtySurv.svg?branch=master)](https://travis-ci.org/vmonaco/frailtySurv)
[![CRAN Downloads](http://cranlogs.r-pkg.org/badges/frailtySurv)](https://CRAN.R-project.org/package=frailtySurv)

## frailtySurv

```{r, echo=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "figures/"
)
```

frailtySurv is an R package for simulating and fitting semiparametric shared frailty models.

## Installation

For the latest stable version, install from CRAN:

```{r eval=F}
install.packages("frailtySurv")
```

The development version can be installed from github using `devtools`.

```{r eval=FALSE}
devtools::install_github("vmonaco/frailtySurv")
```

## Example
The following code shows how to generate data and fit the model.
```{r, echo=TRUE, cache=FALSE}
set.seed(1234)
library(frailtySurv)
dat <- genfrail(N=200, K=2, beta=c(log(2),log(3)), 
                frailty="gamma", theta=2,
                censor.rate=0.35,
                Lambda_0=function(t, tau=4.6, C=0.01) (C*t)^tau)

fit <- fitfrail(Surv(time, status) ~ Z1 + Z2 + cluster(family), 
                dat=dat, frailty="gamma")
```
```{r, echo=TRUE}
fit
```

Parameter traces are given by
```{r, message=FALSE, echo=TRUE, fig.height=3, fig.width=8, cache=FALSE}
plot(fit, type="trace")
```

The estimated cumulative baseline hazard is given by
```{r, message=FALSE, echo=TRUE, fig.height=3, fig.width=8, cache=FALSE}
plot(fit, type="cumhaz")
```

The results can be compared to other estimation techniques.
```{r, message=FALSE, echo=TRUE}
library(survival)
library(frailtypack)
```
```{r, echo=TRUE}
coxph(Surv(time, status) ~ Z1 + Z2 + frailty.gamma(family), data=dat)
frailtyPenal(Surv(time, status) ~ Z1 + Z2 + cluster(family), data=dat, n.knots=10, kappa=2)
```

## Clone and build

You can clone the repository and build the project from source using RStudio. To create a project in RStudio from this repository, you must have both RStudio and git installed.

* In RStudio, go to File -> New Project -> Version Control -> Git
* Name the project (eg. frailtySurv), choose location, and specify the Repository URL as `https://github.com/vmonaco/frailtySurv`

More information about [RStudio and git](https://support.rstudio.com/hc/en-us/articles/200532077-Version-Control-with-Git-and-SVN)

Also see the chapter in the [R packages book](http://r-pkgs.had.co.nz/git.html)

### Build everything

To load the package (simulate installing and loading with `library(frailty)`):
```{r eval=FALSE}
devtools::load_all()
```
or shortuct: **Ctrl+Shift+L**

Use this command to build a source package (binary = FALSE by default)
```{r eval=FALSE}
devtools::build()
```

Other usefull commands and shortcuts:

- Build and reload everything: **Ctrl+Shift+B**
- Check the package, `devtools::check()`: **Ctrl+Shift+E**
- Run all tests, `devtools::test()`: **Ctrl+Shift+T**

### Build vignettes

Build the vignettes with the command:
```{r eval=FALSE}
devtools::build_vignettes()
```

Compiled vignettes will reside in `inst/doc`. In particular, see frailtySurv.pdf

### git pull

Use RStudio to pull the latest code if you've already cloned the repository. In the "git" pane, look for the Pull button. You can also view the commit history from there and see the diff between modified files, if any.